True versus apparent shapes of astrophysical bow shocks

### 2016-01-08 papers/Paper1/sec-application.tex
Insert Radius of curvature description for proplyd model
Advance in section 5

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

Where $I(\theta)\equiv \int^\theta_0 \cos^{1/2}\theta\sin^2\theta$

@@

Expanding (\ref{eq:th1th}) until order 3th around $\theta=0$, we found for $\theta \ll 1$ that $\theta_1\simeq \beta^{1/2}\theta$.

Expanding equation (23) from \citep{Canto:1996} and substituting $\theta_1$ we found that:

\begin{align}
R \simeq R_0 \left(1+\frac{1+2\beta^{1/2}}{6}\theta^2\right)
\label{eq:R_approx}
\end{align}

Which lead us to derive the radius of curvature at the symmetry axis:

\begin{equation}
R_c = \frac{3}{2}R_0\left(1-\beta^{1/2}\right)^{-1}
\label{eq:Rcurv}
\end{equation}

Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).

\begin{figure*}
\includegraphics[width=\linewidth]{rad-vs-beta}
\caption{$R_0$, $R_c$ and $R_{90}$ vsersus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
\label{fig:rad-beta}
\end{figure*}

Observationally, we can measure the projected radii. In order toestimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:radii-r0})

\begin{figure*}
\includegraphics[width=\linewidth]{radii-vs-r0}
\label{fig:radii-r0}
\caption{Left: $R_c$ normalized with $R_0$ vs $R_0$ normalized with $D$. Right:$R_{90}$ normalized with $R_0$ vs $R_0$ normalized with $D$. Since the bow shock brightness decays 
at the wings, it is more difficult to measure $R_{90}$. Along every single curve, $\beta$ is constant. The marks in the curves represents jumps of $15^\circ$ in inclination, and the most left 
mark in each curve represent $i=0^\circ$}
\end{figure*}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
